### 2021-01-03 treatise-pdflatex/4_simulation.tex
Conversion: compile chap 1

Let us represent complex vector and matrices by real ones, consisting of its real and imaginary parts.
For \m {\V {x} \in \mathbb {C} ^{M}}, define the real representation \m {\mathscr {R} \SB {\V {x}}} of \m {\V {x}} to be
%
\DispNum {R:x:R2:M1} {
\mathscr {R} \SB {\V {x}}
\in \mathbb {R} ^{2M} \\
\mathscr {R} \SB {\V {x}} _{\SB {m}}
= \startcases
\mathfrak {Re} \SB {\V {x} _{\SB {m'}}}, \MC m =2m' \\
\mathfrak {Im} \SB {\V {x} _{\SB {m'}}}, \MC m =2m'+1 \\
\stopcases \\
m' 
=  0, 1, 2, \ldots, M-1 \\
}
%
The injection is obvious, and we may define \m {\mathscr {R} ^{-1}} so that
%
\DispNum {R:1:x::x:} {
\mathscr {R} ^{-1} \SB {\mathscr {R} \SB {\V {x}}}
=\V {x} \\
}
%
Accordingly, the following generalization to complex matrices is valid, once we call the ring representation of complex numbers.
For \m {\M {A} \in \mathbb {C} ^{M_1 \D M_2}}, define real representation \m {\mathscr {R} \SB {\M {A}}} of \m {\M {A}} to be
%
\DispNum {R:A:R2:21} {
\mathscr {R} \SB {\M {A}}
\in \mathbb {R} ^{2M_1 \D 2M_2} \\
\mathscr {R} \SB {\M {A}} _{\SB {m_1,m_2}} =
\startcases
\mathfrak {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1', 2m_2'} \\
\mathfrak {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'} \\
-\mathfrak {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1', 2m_2'+1} \\
\mathfrak {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'+1} \\
\stopcases \\
m_1 
= 0, 1, 2, \ldots, M_1 -1 \\
m_2 
= 0, 1, 2, \ldots, M_2 -1 \\
}

@@

\DispNum {y:y:Ry:Ny} {
\tilde {\V {y}}
= \mathscr {R} \SB {\V {y}}
\in \mathbb {R} ^{2 N_B^2} \\
%
\tilde {\V {g}}
= \mathscr {R} \SB {\V {g}}
\in \mathbb {R} ^{2 N_H^2} \\
%
\tilde {\M {P}}
= \mathscr {R} \SB {\M {P}}
\in \mathbb {R} ^{2 N_B^2 \D 2 N_H^2} \\
%
\tilde {\M {P}} ^\Adj
= \mathscr {R} \SB {\M {P} ^\Adj}
\in \mathbb {R} ^{2 N_B^2 \D 2 N_H^2} \\
%
\tilde {\V {z}}
= \mathscr {R} \SB {\V {z}}
\in \mathbb {R} ^{2 N_B^2} \\
}
%
so, by construction,
%
\DispNum {y:y:Pg:gz} {
\V {\tilde {y}}
= \M {\tilde {P}} \V {\tilde {g}} +\V {\tilde {z}} \\
}
%
And denote \m {\V {1}} to be the all-\m{1} vector, and \m {\V {0}} the all-\m{0} vector, whose dimension will be inferred from context.

@@

\Result
{Algorithm}
{
\startitemize[n]
\item Input \m{\M {P} \in \mathbb {C} ^{ N_B^2 \D N_H^2}}, \m{\V {y} \in \mathbb {C} ^{ N_B^2}}, \m {\g_{\mathrm {DS}} > 0}.
%
\item Define \m {\tilde {\V {y}}, \tilde {\V {g}}, \tilde {\M {P}}, \tilde {\M {P}} ^\Adj, \tilde {\V {z}}}, according to \Rf {y:y:Ry:Ny}.
%
\item Compute the convex program
\DispNum {g:f:gf:S1} {
\hat {\tilde {\V {g}}}, \hat {\tilde {\V {f}}}
\leftarrow \startcases
   \Min {\tilde {\V {g}}', \tilde {\V {f}}'}  \MC \IP {\V {1}, \tilde {\V {f}}'} \\
   \mathrm {subject} \; \mathrm {to} \MC \tilde {\V {g}}' \preceq \tilde {\V {f}}' \\
   \MC - \tilde {\V {g}}' \preceq \tilde {\V {f}}' \\
   \MC \tilde {\M {P}}^\dagger \tilde {\M {P}} \tilde {\V {g}}' \preceq \tilde {\M {P}}^\dagger \tilde {\V {y}} + \g_{\mathsf {DS}} \V {1} \\
   \MC - \tilde {\M {P}}^\dagger \tilde {\M {P}} \tilde {\V {g}}' \preceq - \tilde {\M {P}}^\dagger \tilde {\V {y}} + \g_{\mathsf {DS}} \V {1} \\
\stopcases \\
}
\item Convert
%
\DispNum {g:::R1:1g} {
\Hat{\V {g}}
\leftarrow \mathscr {R} ^{-1} \SB {\Hat{\T{\V {g}}}} \\
}
\item Calculate
%
\DispNum {G:G:ve:1g} {
\hat {G}
\leftarrow \mathrm {vec}^{-1} \SB {\hat {g}} \\
}
\item Calculate
%
\DispNum {H:H:KG:GK} {
\hat {\M {H}}
\leftarrow \M {K} \hat {\M {G}} \M {K}^\dagger \\
}
\item Output \m {\hat {\M {H}}}.
\stopitemize
}

@@

Every Newton step involves a inversion of \m {\mathscr {O} \SB {\M {P} ^\dagger \M {P}}}, having the same order of magnitude to the time needed for matrix multiplication.
Since the dimension of \m {\M {P} ^\dagger \M {P}} is \m {N_H^2}, the cost of inversion may be roughly considered to be \m {\mathscr {O} \SB {N_H^4}}, as we know from newer results on the complexity of matrix inversion.
That is, we suppose \m {C_{\mathrm {step}} = N_H^4}.

We take some liberty to assume that, at the start the iteration, the Moore–Penrose inverse was taken to be the initial value of \m {\V {g}_0}, namely
%
\DispNum {g:0:gL:Py} {
\V {g}_0
=\V {g}_{\mathrm {LS}} \\
= \RB {\M {P} ^\dagger \M {P}} ^{-1} \M {P} ^\dagger \V {y} \\
}
%
By above, we may write the complexity of DS to be
%
\DispNum {C:S:Og:g1} {
C_{\mathrm {DS}}
=\mathscr {O} \SB {\VNm {\V {g}_{\mathrm {LS}} -\V {g} ^\star} _1} N_H^4 \\
}
%
Also assume
%
\DispNum {g:g:g;:;g} {
\V {g} ^\star
\approx \V {g} \\
}
%
Indeed, this is the main thesis of our investigation.
And by restricted isometry, \m {\M {P}} has unity-normed, almost orthogonal columns, so
%
\DispNum {P:P:IN:H2} {
\M {P} ^\dagger \M {P}
\approx I _{N_{H}^2} \\
}
%
Thus, by \Rf {g:0:gL:Py}, \Rf {C:S:Og:g1}, and \Rf {g:g:g;:;g},
%
\DispNum {C:S:Og:z1} {
C_{\mathrm {DS}}
=\mathscr {O} \SB {
   \VNm {\V {g} +\RB {\M {P} ^\dagger \M {P}} ^{-1} \M {P} ^\dagger \V {z}
   -\V {g}} _1} N_H^4 \\
=\mathscr {O} \SB {\VNm {\M {P} ^\dagger \V {z}} _1} N_H^4 \\
}

We see that \m {\RB {\M {P} ^\dagger \V {z}} _{\SB {j}}} observes complex standard normal distribution.
If we agree that, for high probability,
%
\DispNum {O:j:sO:O1} {
\mathscr {O} \SB {\VNm {\M {P} ^\dagger \V {z}} _{\SB {j}}}
= \s \mathscr {O} \RB {1} \\
}
Then we simply have
%
\DispNum {C:S:ON:H6} {
C_{\mathrm {DS}}
=\mathscr {O} \SB {N_{H}^6} \\
}

On the other hand, Tropp and Gilbert \cite {TrG07a} discussed the complexity of OMP in the companion paper \cite {TrG07b}.
They gave
%
\DispNum {C:P:ON:NY} {
C_{\mathrm {OMP}}
=\mathscr {O} \SB {N_H^2 \log N_B} \\
}
%
Here \m {\log N_B} is small in our experiments, and if we dropped some constants and \m {\log N_B}, then we may assume \m {\mathscr {O} \SB {N_H^2}}.

Lastly, since Lasso involves the same target function as DS, the same argument is valid, giving \m {C_{\mathrm {Lasso}} =\mathscr {O} \SB {N_H^6}}.

@@

\DispNum {t:P:NH:83} {
\tilde {t}_{\mathrm {OMP}} \eqsim \mathscr {O} \SB {N_H^{3.6}} \\
\tilde {t}_{\mathrm {Lasso}} \eqsim \mathscr {O} \SB {N_H^{4.8}} \\
\tilde {t}_{\mathrm {DS}} \eqsim \mathscr {O} \SB {N_H^{8.3}} \\
}

>>>>

Let us represent complex vector and matrices by real ones, consisting of its real and imaginary parts.
For \m {\V {x} \in \mathbb {C} ^{M}}, define the real representation \m {\mathcal {R} \SB {\V {x}}} of \m {\V {x}} to be
%
\DispNum {R:x:R2:M1} {
\mathcal {R} \SB {\V {x}}
\in \mathbb {R} ^{2M} \\
\mathcal {R} \SB {\V {x}} _{\SB {m}}
= \startcases
\mathfrak {Re} \SB {\V {x} _{\SB {m'}}}, \MC m =2m' \\
\mathfrak {Im} \SB {\V {x} _{\SB {m'}}}, \MC m =2m'+1 \\
\stopcases \\
m' 
=  0, 1, 2, \ldots, M-1 \\
}
%
The injection is obvious, and we may define \m {\mathcal {R} ^{-1}} so that
%
\DispNum {R:1:x::x:} {
\mathcal {R} ^{-1} \SB {\mathcal {R} \SB {\V {x}}}
=\V {x} \\
}
%
Accordingly, the following generalization to complex matrices is valid, once we call the ring representation of complex numbers.
For \m {\M {A} \in \mathbb {C} ^{M_1 \D M_2}}, define real representation \m {\mathcal {R} \SB {\M {A}}} of \m {\M {A}} to be
%
\DispNum {R:A:R2:21} {
\mathcal {R} \SB {\M {A}}
\in \mathbb {R} ^{2M_1 \D 2M_2} \\
\mathcal {R} \SB {\M {A}} _{\SB {m_1,m_2}} =
\startcases
\mathfrak {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1', 2m_2'} \\
\mathfrak {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'} \\
-\mathfrak {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1', 2m_2'+1} \\
\mathfrak {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'+1} \\
\stopcases \\
m_1 
= 0, 1, 2, \ldots, M_1 -1 \\
m_2 
= 0, 1, 2, \ldots, M_2 -1 \\
}

@@

\DispNum {y:y:Ry:Ny} {
\tilde {\V {y}}
= \mathcal {R} \SB {\V {y}}
\in \mathbb {R} ^{2 N_B^2} \\
%
\tilde {\V {g}}
= \mathcal {R} \SB {\V {g}}
\in \mathbb {R} ^{2 N_H^2} \\
%
\tilde {\M {P}}
= \mathcal {R} \SB {\M {P}}
\in \mathbb {R} ^{2 N_B^2 \D 2 N_H^2} \\
%
\tilde {\M {P}} ^\Adj
= \mathcal {R} \SB {\M {P} ^\Adj}
\in \mathbb {R} ^{2 N_B^2 \D 2 N_H^2} \\
%
\tilde {\V {z}}
= \mathcal {R} \SB {\V {z}}
\in \mathbb {R} ^{2 N_B^2} \\
}
%
so, by construction,
%
\DispNum {y:y:Pg:gz} {
\V {\tilde {y}}
= \M {\tilde {P}} \V {\tilde {g}} +\V {\tilde {z}} \\
}
%
And denote \m {\V {1}} to be the all-\m{1} vector, and \m {\V {0}} the all-\m{0} vector, whose dimension will be inferred from context.

@@

\Result
{Algorithm}
{
\startitemize[n]
\item Input \m{\M {P} \in \mathbb {C} ^{ N_B^2 \D N_H^2}}, \m{\V {y} \in \mathbb {C} ^{ N_B^2}}, \m {\g_{\mathrm {DS}} > 0}.
%
\item Define \m {\tilde {\V {y}}, \tilde {\V {g}}, \tilde {\M {P}}, \tilde {\M {P}} ^\Adj, \tilde {\V {z}}}, according to \Rf {y:y:Ry:Ny}.
%
\item Compute the convex program
\DispNum {g:f:gf:S1} {
\hat {\tilde {\V {g}}}, \hat {\tilde {\V {f}}}
\leftarrow \startcases
   \Min {\tilde {\V {g}}', \tilde {\V {f}}'}  \MC \IP {\V {1}, \tilde {\V {f}}'} \\
   \mathrm {subject} \; \mathrm {to} \MC \tilde {\V {g}}' \preceq \tilde {\V {f}}' \\
   \MC - \tilde {\V {g}}' \preceq \tilde {\V {f}}' \\
   \MC \tilde {\M {P}}^\dagger \tilde {\M {P}} \tilde {\V {g}}' \preceq \tilde {\M {P}}^\dagger \tilde {\V {y}} + \g_{\mathsf {DS}} \V {1} \\
   \MC - \tilde {\M {P}}^\dagger \tilde {\M {P}} \tilde {\V {g}}' \preceq - \tilde {\M {P}}^\dagger \tilde {\V {y}} + \g_{\mathsf {DS}} \V {1} \\
\stopcases \\
}
\item Convert
%
\DispNum {g:::R1:1g} {
\Hat{\V {g}}
\leftarrow \mathcal {R} ^{-1} \SB {\Hat{\T{\V {g}}}} \\
}
\item Calculate
%
\DispNum {G:G:ve:1g} {
\hat {G}
\leftarrow \mathrm {vec}^{-1} \SB {\hat {g}} \\
}
\item Calculate
%
\DispNum {H:H:KG:GK} {
\hat {\M {H}}
\leftarrow \M {K} \hat {\M {G}} \M {K}^\dagger \\
}
\item Output \m {\hat {\M {H}}}.
\stopitemize
}

@@

Every Newton step involves a inversion of \m {\mathcal {O} \SB {\M {P} ^\dagger \M {P}}}, having the same order of magnitude to the time needed for matrix multiplication.
Since the dimension of \m {\M {P} ^\dagger \M {P}} is \m {N_H^2}, the cost of inversion may be roughly considered to be \m {\mathcal {O} \SB {N_H^4}}, as we know from newer results on the complexity of matrix inversion.
That is, we suppose \m {C_{\mathrm {step}} = N_H^4}.

We take some liberty to assume that, at the start the iteration, the Moore–Penrose inverse was taken to be the initial value of \m {\V {g}_0}, namely
%
\DispNum {g:0:gL:Py} {
\V {g}_0
=\V {g}_{\mathrm {LS}} \\
= \RB {\M {P} ^\dagger \M {P}} ^{-1} \M {P} ^\dagger \V {y} \\
}
%
By above, we may write the complexity of DS to be
%
\DispNum {C:S:Og:g1} {
C_{\mathrm {DS}}
=\mathcal {O} \SB {\VNm {\V {g}_{\mathrm {LS}} -\V {g} ^\star} _1} N_H^4 \\
}
%
Also assume
%
\DispNum {g:g:g;:;g} {
\V {g} ^\star
\approx \V {g} \\
}
%
Indeed, this is the main thesis of our investigation.
And by restricted isometry, \m {\M {P}} has unity-normed, almost orthogonal columns, so
%
\DispNum {P:P:IN:H2} {
\M {P} ^\dagger \M {P}
\approx I _{N_{H}^2} \\
}
%
Thus, by \Rf {g:0:gL:Py}, \Rf {C:S:Og:g1}, and \Rf {g:g:g;:;g},
%
\DispNum {C:S:Og:z1} {
C_{\mathrm {DS}}
=\mathcal {O} \SB {
   \VNm {\V {g} +\RB {\M {P} ^\dagger \M {P}} ^{-1} \M {P} ^\dagger \V {z}
   -\V {g}} _1} N_H^4 \\
=\mathcal {O} \SB {\VNm {\M {P} ^\dagger \V {z}} _1} N_H^4 \\
}

We see that \m {\RB {\M {P} ^\dagger \V {z}} _{\SB {j}}} observes complex standard normal distribution.
If we agree that, for high probability,
%
\DispNum {O:j:sO:O1} {
\mathcal {O} \SB {\VNm {\M {P} ^\dagger \V {z}} _{\SB {j}}}
= \s \mathcal {O} \RB {1} \\
}
Then we simply have
%
\DispNum {C:S:ON:H6} {
C_{\mathrm {DS}}
=\mathcal {O} \SB {N_{H}^6} \\
}

On the other hand, Tropp and Gilbert \cite {TrG07a} discussed the complexity of OMP in the companion paper \cite {TrG07b}.
They gave
%
\DispNum {C:P:ON:NY} {
C_{\mathrm {OMP}}
=\mathcal {O} \SB {N_H^2 \log N_B} \\
}
%
Here \m {\log N_B} is small in our experiments, and if we dropped some constants and \m {\log N_B}, then we may assume \m {\mathcal {O} \SB {N_H^2}}.

Lastly, since Lasso involves the same target function as DS, the same argument is valid, giving \m {C_{\mathrm {Lasso}} =\mathcal {O} \SB {N_H^6}}.

@@

\DispNum {t:P:NH:83} {
\tilde {t}_{\mathrm {OMP}} \eqsim \mathcal {O} \SB {N_H^{3.6}} \\
\tilde {t}_{\mathrm {Lasso}} \eqsim \mathcal {O} \SB {N_H^{4.8}} \\
\tilde {t}_{\mathrm {DS}} \eqsim \mathcal {O} \SB {N_H^{8.3}} \\
}
